Large-scale feature selection with Gaussian mixture models for remote sensing images

### 2016-10-14 paper.tex
derniere relecture
interrompu au critere OA, Kappa ...

\IEEEPARstart{W}{ith} the increasing number of remote sensing missions, the quantity of available Earth observation data for a given landscape becomes larger and larger. Satellite missions produce a huge amount of data on a regularly (daily) basis. From 2018, the EnMAP (Environmental Mapping and Analysis Program) satellites managed by the German space agency will produce images with 244 spectral bands, a spatial resolution of 30x30m per pixel and with a frequency of revisit of 4 days\cite{Müller09enmap}. The Hyperspectral Infrared Imager (HyspIRI) of NASA will also deliver images with 212 spectral bands. Additionally to hyperspectral data, the amount of available hypertemporal data increases a lot. For instance, the European satellites Sentinel-2 were launched successfully recently and 2 Terabytes of data will be released every days~\cite{drusch2012sentinel}. The Landsat open archive (\url{http://landsat.usgs.gov/products_data_at_no_charge.php}) has released thousands of images. This high volume of Earth observation data provides an accurate information of land state and functioning, and helps to improve the understanding of the planet~\cite{rs1010001}. However, processing such data is more and more challenging because of statistical and computational issues.

@@

There  are  two  main  strategies  to  reduce  dimension~\cite[Chapter
1]{Guyon:2006:FEF:1208773}: features extraction and feature selection.
Feature extraction means reformulate  and summarize the information by
creating new features in combining  the existing ones, it is sometimes
referred to as \emph{feature construction}.   Linear combination  of the
initial features  can be extracted using  Principal Component Analysis
(PCA)~\cite{jimenez1998supervised}  or Independent  Component Analysis
\cite{villa2011hyperspectral}.  Supervised extraction  method has also
been investigated  such as Fischer discriminant  analysis and decision
boundary feature  extraction~\cite{book:landgrebe}.  To  the contrary,
features selection  extracts a subset of  existing features identified
as the  most relevant  by a  given criterion.   It has  the additional
advantage to be much more easily understandable for the end-user.

@@

The third class corresponds to the \emph{embedded methods}. They do not separate the features selection process from the learning algorithm and allow interaction between the two processes. A popular method embedded method is the \emph{Random Forest}. Embedded methods also exist for other models, \emph{e.g.} SVM \cite{guyon2002gene,weston2003use,tuia2015multiclass}.

@@

The remaining of the article is organized as follows. Section~\ref{sec:gmm-hd} presents GMM classifiers and the problems related to high-dimensional feature spaces. The features selection methods are detailed in Section~\ref{sec:selection}. Then an efficient implementation of the proposed selection method is presented in Section~\ref{sec:implementation}. Experimental results on two real high dimensional data-set are given Section~\ref{sec:test}. Conclusion and perspectives conclude the paper in Section~\ref{sec:conclusion}.

@@

        A measure of correct classification is based on an error matrix $M$, or \emph{confusion matrix}~\cite[Chapter 4]{congalton2008assessing}. The confusion matrix allows the computation of several global and per-class indices related to the classification accuracy~\cite{congalton2008assessing}. Three global criteria were used:

>>>>

\IEEEPARstart{W}{ith} the increasing number of remote sensing missions, the quantity of available Earth observation data for a given landscape becomes larger and larger. Satellite missions produce a huge amount of data on a regularly (daily) basis. From 2018, the EnMAP (Environmental Mapping and Analysis Program) satellites managed by the German space agency will produce images with 244 spectral bands, a spatial resolution of 30x30m per pixel and with a frequency of revisit of 4 days\cite{Müller09enmap}. The Hyperspectral Infrared Imager (HyspIRI) of NASA will also deliver images with 212 spectral bands. Additionally to hyperspectral data, the amount of available hypertemporal data increases a lot. For instance, the European satellites Sentinel-2 were launched recently and 2 Terabytes of data will be released every day~\cite{drusch2012sentinel}. The Landsat open archive (\url{http://landsat.usgs.gov/products_data_at_no_charge.php}) has released thousands of images. Such high volume of Earth observation data provides an accurate information of land state and functioning, and helps to improve the understanding of the planet~\cite{rs1010001}. However, processing such data is more and more challenging because of statistical and computational issues.

@@

There  are  two  main  strategies  to  reduce  dimension~\cite[Chapter
1]{Guyon:2006:FEF:1208773}: features extraction and feature selection.
Feature extraction means reformulate  and summarize the information by
creating new features in combining  the existing ones, it is sometimes
referred to as \emph{feature construction}.  Linear combination of the
initial features  can be extracted using  Principal Component Analysis
(PCA)~\cite{jimenez1998supervised}  or Independent  Component Analysis
\cite{villa2011hyperspectral}.  Supervised extraction  method has also
been investigated  such as Fischer discriminant  analysis and decision
boundary feature  extraction~\cite{book:landgrebe}.  To  the contrary,
features selection  extracts a subset of  existing features identified
as  the most  relevant  by a  given criterion.   This  subset has  the
additional advantage to  be much more understandable  for the end-user
than those constructed by a (non-)linear combination.

@@

The third class corresponds to the \emph{embedded methods}. They do not separate the features selection process from the learning algorithm and allow interaction between the two processes. A popular embedded method is the \emph{Random Forest}. Embedded methods also exist for other models, \emph{e.g.} SVM \cite{guyon2002gene,weston2003use,tuia2015multiclass}.

@@

The     remaining    of     the     article     is    organized     as
follows.   Section~\ref{sec:gmm-hd}  presents   GMM  classifiers   and
problems  related to  high-dimensional  feature  spaces. The  features
selection methods are detailed in Section~\ref{sec:selection}. Then an
efficient         implementation        is         presented        in
Section~\ref{sec:implementation}.  Experimental  results on  two  real
high dimensional data-set are given Section~\ref{sec:test}. Conclusion
and perspectives conclude the paper in Section~\ref{sec:conclusion}.

@@

        A measure of correct classification is based on an error matrix $M$, or \emph{confusion matrix}~\cite[Chapter 4]{congalton2008assessing}. The confusion matrix allows the computation of several global and per-class indices related to the classification accuracy~\cite{congalton2008assessing}. Three global criteria were used in this work:
